Supplement to: Assessing the impact of urban heating on tree growth in Berlin with open inventory and environmental data

### 2022-10-11 analysis/paper/paper.Rmd
rendering

Several urban tree species have been shown to have tendencies of enhanced growth rates and/or productivity compared to rural conspecifics [e.g., @briber2015; @obrien2012], which is typically attributed to increased temperatures [@jia2018; @pretzsch2017], however, a broad range of effect sizes and signs (i.e., reduced growth) specific to species and location are also commonly reported alongside.

@@

\begin{equation}
D(y, \hat{\mu}) = 2 \cdot \left\{ \frac{y−\hat{\mu}}{\hat{\mu}}  − log(\frac{y}{\hat{\mu}}) \right\}

(\#eq:gam-deviance)
\end{equation}

>>>>

Several urban tree species have been shown to have tendencies of enhanced growth rates and/or productivity compared to rural conspecifics [e.g., @briber2015; @obrien2012], which is typically attributed to increased temperatures [@jia2018; @pretzsch2017], however, a broad range of effect sizes and signs (i.e., reduced growth) specific to species and location are also commonly reported alongside [e.g., @berland2020].

@@

\begin{equation}
D(y, \hat{\mu}) = 2 \cdot \left\{ \frac{y−\hat{\mu}}{\hat{\mu}}  − log(\frac{y}{\hat{\mu}}) \right\}
(\#eq:gam-deviance)
\end{equation}

### 2022-10-11 analysis/paper/supplemental_information.Rmd
rendering

---
title: "Supplement to: Assessing the impact of urban heating on tree growth in Berlin with open inventory and environmental data"
author:
  - Alexander G. Hurley$^{a *}$, Ingo Heinrich$^a$
  - $^a$ *Geoforschungszentrum Potsdam, Section 4.3, Germany*
  - "* Corresponding author: hurley@gfz-potsdam.de"
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: true
output: 
    bookdown::html_document2:
      fig_caption: yes
      toc: true
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage[normalem]{ulem}
bibliography: 
  - uhi_references.bib
  - 04_gfz_UHI.bib
  - 07_phenoTram.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style

@@

>>>>

---
title: "Supplement to: Assessing the impact of urban heating on tree growth in Berlin with open inventory and environmental data"
author:
  - Alexander G. Hurley$^{a *}$, Ingo Heinrich$^a$
  - $^a$ *Geoforschungszentrum Potsdam, Section 4.3, Germany*
  - "* Corresponding author: hurley@gfz-potsdam.de"
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: true
output: 
    bookdown::html_document2:
      fig_caption: yes
      toc: true
toc-title: "Table of Contents"
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage[normalem]{ulem}
bibliography: 
  - uhi_references.bib
  - 04_gfz_UHI.bib
  - 07_phenoTram.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style

@@

# References
